Uncertainty on the galaxy-halo connection for Lyman-$\alpha$ emitters at $z=3.1$

### 2016-03-30 paper/ms.tex
revisando results + discussion

% JF - 1. Intro 3/10
% JF - 2. Methodology 1/7

@@

%JF

@@

\subsection{A model to populate halos with LAEs}
\label{subsec:mocks}

@@

\subsection{Exploring and selecting consistent models}
\label{subsec:explore}

@@

We put a flat prior on $\log M_{\rm min}$ and $\log \mmax$ between
$9.2$ up to $13.4$, corresponding to the halo mass range of 
the simulation at $z=3$.  
We restrict the selection to models that give a minimal number denity $N_{\rm{halos}}>N_{\rm
  LAE}/3$.  
This means that it is possible to have $N_{\rm
  {halos}} < N_{\rm LAE}$ and hence $\focc\equiv N_{\rm LAE}/N_{\rm
  halo}>1$.  
This only reflects the uncertainty in the number 
density of LAEs due to cosmic variance.

@@

\section{Results and Discussion}

\subsection{Constraining \mmin, \mmax\ and \focc\ in Dark Matter Halos hosting LAEs}

In Fig. \ref{fig:like} we present yhe one and two dimensional
projections of the posterior probability distributions of \mmin, \mmax
and \focc. We find that the \mmin and \mmax parameter space cannot be
tightly constrained mainly because of cosmic variance and the large
observational Poisonnian uncertainty in the ACF. We however found that
9.6$<\log \mmin<$11.0 and 10.9$<\log\mmax<$13.0.   We interestingly
find that \focc\ is basically completely determined by \mmin  going
from \focc$=$0.015 when $\log\mmin=$9.6 to \focc$=$0.30 when
$\log\mmin=$11.0
($\focc\sim0.1\left(\mmin/10^{10.5}\right)^{0.93}$). We remark that
those models where $\log \focc>0.00$ ($\focc>1$) correspond  to models where the number density  of halos is smaller than the number of observed LAEs but are
still consistent because of the uncertainty in the median number
density of LAEs in the universe due to cosmic variance (see
Fig. \ref{fig:cosmicv0} and \S\ref{subsec:explore}).%in the number of dark matter halos along the
                         %mock fields

@@

\subsection{Halo mass distribution within models}

Previous  attempts to constrain the DMH mass of LAEs by means of the
ACF   present their result in terms of the median mass of LAEs that is
derived from the derived correlation length by means of
semi-analitical prescriptions
\citep[e.g.][]{Hayashino2004,Gawiser2007,Ouchi2010,Bielby16}. Instead,
in this work we directly compare the ACF of our simulated mock
catalogs with the observational ACF and present our results in terms
of a  minimum and maximum mass DMH hosting LAEs. It is therefore
necessary to connect our approach by computing the median mass of the
DMH in each of the models $\mathcal{M}$.  In   Fig. \ref{fig:mmed} we
show the 50 ($\log M_{50}$, black dots), the 84 ($\log M_{84}$,blue
diamonds) and 95 ($\log M_{95}$, red squares) percentiles of the LAE
halo mass as a function of \lmmin\ for each of the models that we run
in our MCMC simulation.  The points are color coded according to their
\dlm\ associated value. We can see that the median mass ($M_{50}$) and
$M_{84}$ are not very sensitive to  $\lmmax=\lmmin +\dlm$ specially
when $\dlm\gtrsim1.0$dex. We particularly found that
$\lmmin\lesssim\log M_{50}\lesssim\lmmin+0.2\rm{dex}$ and that
$\lmmin+0.1\rm{dex}\lesssim\log M_{50}\lesssim\lmmin+0.5\rm{dex}$
regardless of the value of \dlm. The latter is a consequence of the
very steepen distribution of the dark matter mass function  and is at
the same time the reason for the almost perfect one to one relation
between \mmin\ and \focc. However, it can also be seen in
Fig. \ref{fig:mmed} that $\log M_{84}$ is very sensitive to \lmmax
($\lmmin+0.2\rm{dex}\lesssim\log
M_{50}\lesssim\lmmin+1.5\rm{dex}$). Thereby, any differences in the
clustering strength of models sharing the same \mmin but different
\mmax should be mainly driven by the  $\sim16\%$ most massive  halos
of each model $\mathcal{M}$.

>>>>

@@

@@

\subsection{A simple LAE model}
\label{subsec:mocks}

@@

\subsection{Model Selection}
\label{subsec:explore}

@@

We put a flat prior on $\log M_{\rm min}$ and $\log \mmax$ between
$9.2$ up to $13.4$, corresponding to the halo mass range of 
the simulation at $z=3$.  
We restrict the selection to models that give a minimal number density 
$N_{\rm{halos}}>N_{\rm LAE}/3$.   
This means that it is possible to have $N_{\rm{halos}} < N_{\rm LAE}$
and hence $\focc\equiv N_{\rm{LAE}}/N_{\rm{halos}}>1$.   
This only reflects the uncertainty in the number 
density of LAEs due to cosmic variance.

@@

\section{Results and Discussion}
\label{sec:results}

\subsection{Constraints on Model Parameters}

Fig. \ref{fig:like} shows the one and two dimensional projections of
the posterior probability distributions of the parameters in our LAE model. 
This Figure represents our main result: \mmin, \mmax\  and \focc\ cannot
be tightly constrained from the available observations.

The preferred $1-\sigma$ range for the masses is $9.6<\log \mmin<11.0$
and $10.9<\log\mmax<13.0$.
\focc\ is completely determined by \mmin\ from \focc$=$0.015 when
$\log\mmin=9.6$ to $\focc=0.30$ when $\log\mmin=11.0$. 
We compute the power-law dependece between \focc\ and \mmin\ to be 
\begin{equation}
\focc = 0.1\left(\frac{\mmin}{10^{10.5}\hMsun}\right)^{0.93}.
\end{equation}
We remind to the reader that models whith $\log \focc>0.00$ ($\focc>1$)
correspond to cases where the halo number density is smaller 
than the number of observed LAEs but are  still consistent because of
the uncertainty in the median number density of LAEs in the universe
due to cosmic variance (see Fig. \ref{fig:cosmicv0} and
\S\ref{subsec:explore}).

@@

\subsection{Median Halo Mass Within Models}

We now compute the median mass, $\log M_{50}$, of the LAE hosting halos for each model
$\mathcal{M}$; $\log M_{50}$ allows a direct comparison between our
results and previous results in the literature
\citep[e.g.][]{Hayashino2004,Gawiser2007,Ouchi2010,Bielby16} that used
a more simplified approach.

In   Fig. \ref{fig:mmed} we
show the 50 ($\log M_{50}$, black dots), the 84 ($\log M_{84}$,blue
diamonds) and 95 ($\log M_{95}$, red squares) percentiles of the LAE
halo mass as a function of \lmmin\ for each of the models that we run
in our MCMC simulation.  The points are color coded according to their
\dlm\ associated value. We can see that the median mass ($M_{50}$) and
$M_{84}$ are not very sensitive to  $\lmmax=\lmmin +\dlm$ specially
when $\dlm\gtrsim1.0$dex. We particularly found that
$\lmmin\lesssim\log M_{50}\lesssim\lmmin+0.2\rm{dex}$ and that
$\lmmin+0.1\rm{dex}\lesssim\log M_{50}\lesssim\lmmin+0.5\rm{dex}$
regardless of the value of \dlm. The latter is a consequence of the
very steepen distribution of the dark matter mass function  and is at
the same time the reason for the almost perfect one to one relation
between \mmin\ and \focc. However, it can also be seen in
Fig. \ref{fig:mmed} that $\log M_{84}$ is very sensitive to \lmmax
($\lmmin+0.2\rm{dex}\lesssim\log
M_{50}\lesssim\lmmin+1.5\rm{dex}$). Thereby, any differences in the
clustering strength of models sharing the same \mmin but different
\mmax should be mainly driven by the  $\sim16\%$ most massive  halos
of each model $\mathcal{M}$.
